---
title: "Homework 2 R-couchdb and patient encounters"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Part 3 - R, CoucDB, and Patient Encounters (8 points)
Knit the results and paste them in the final Word document!

Load library RJSONIO, R4CouchDB, and httr
```{r include=TRUE}
library("RJSONIO")
library("R4CouchDB")
library("httr")
```
### Q3.1. I prepared a database on CouchDB from our patient encounter dataset. I would like you to get the total number of documents in this database (1 point)
- HINT: `http://18.216.66.226:5984/patient_enc`
- HINT: field name is `doc_count` 
- HINT: N=2918
```{r}
# Get the URL
serverUrl <- "http://18.216.66.226:5984/patient_enc"
res <- GET(serverUrl)

# Print document count for patient_enc
content(res)$doc_count

```

### Q3.2. CREATE a new patient encounter (R4CouchDB) (1 point)
Please use `0x00S2018hw2{your username}` as the id, e.g. `0x00S2018hw2wutz`, and the encounter should have the same values as encounter `0x001498BC28E96026` with different `_id` and `_rev`.

- HINT: username = your 6+2 id, password = your first name, all lower case, with no special charaters and space
- HINT: the database name is `patient_enc`, not `patient`
- HINT: check the encounter you create at `http://18.216.66.226:5984/patient_enc/{id}`
- HINT: if you have created the enconuter, delete the encounter before recreating it using
```{r}
pid = '0x00S2018hw2lapema'

# Make connection to db server!
cdb <- cdbIni(serverName="18.216.66.226",DBName="patient_enc",prot="http",port=5984,uname="lapema",pwd="michael")

# Copy the data from 0x001498BC28E96026
cdb$dataList <- list(dept_nm="UH RADIOLOGY",pat_id="0x01F089080FE0",
                     gender="Female", age="49", primary_loc= "UCP WYOMING")

# Assign my id to this new record
cdb$id = pid

# Add my new document that has the data from 0x001498BC28E96026 and my new ID.
cdb <- cdbAddDoc(cdb)
```

### Q3.3. READ this encounter by id, pull the age value (R4CouchDB) (1 point)
```{r include=TRUE}
# Get the document by this pid
cdb$id <- pid
cdb <- cdbGetDoc(cdb)

# Extract the result and print the age
rec <- cdb$res
rec$age
```
### Q3.4. UPDATE this encounter by id, add patient DoB `1969-03-05` (R4CouchDB) (1 point)
```{r}
# Get the document by this pid
cdb$id <- pid
cdb <- cdbGetDoc(cdb)

# Add dob to this document and push the update.
cdb$dataList$dob <- "1969-03-05"
cdb <- cdbUpdateDoc(cdb)

```

### Q3.5. READ this encounter by id again, pull the DoB value (R4CouchDB) (1 point)
```{r include=TRUE}
# Get the document by this pid
cdb$id <- pid
cdb <- cdbGetDoc(cdb)

# Print dob value
cdb$dataList$dob
```

### Q3.6. REMOVE the DoB field of this encounter (R4CouchDB) (1 point)
```{r}
# Get the document by this pid
cdb$id <- pid
cdb <- cdbGetDoc(cdb)

# Set DOB to Null and push update
cdb$dataList$dob <- NULL
cdb <- cdbUpdateDoc(cdb)
```

### Q3.7. SEARCH and LIST all encounters of patient `0x01F089080FE0` (RESTFul), and only show the number of encounters (length, N=11) (1 point)
```{r}
# Our search param
param <- list(selector=list(pat_id="0x01F089080FE0"))

# URL to submit our post to 
findUrl <- paste(serverUrl,"/_find",sep="") 

# run the POST and store return
response <- POST(findUrl,body=param,encode="json")

# Pull the content out of the response, and 'decode' the JSON.
out <- content(response,"text",encoding="UTF-8")
out <- fromJSON(out)

# Only show the number of encounters = length of docs found
length(out$docs)
```

### Q3.8. DELETE the encounter by ID (1 point)
```{r}
cdb$id <- pid
cdb <- cdbDeleteDoc(cdb)
```
